---
title: "hw_02"
author: "justyn koenig"
date: "10/4/2021"
output: 
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Question 1 

```{r}
mtcars[mtcars$cyl < 6, ]

mtcars[1:3, ]

mtcars[mtcars$cyl == 8,]

mtcars[mtcars$cyl %% 4 == 0 | mtcars$cyl == 6,]

```


# Question 2


The code generates five missing values, because x represents 5 different numbers (1, 2, 3, 4, 5). This means that when x is assigned NA, the output will be NA for (1, 2, 3, 4, 5) which results in 5 different missing values (NA, NA, NA, Na, NA). 




# Question 3 


mtcars[1:15] returns an error because there is no comma then space after 15.There is a undefined columns being selected. You need to write the code as mtcars[1:15, ] because you code the 1D index for each dimension and SEPERATE them by a comma.This identifies which columns are being selected. 




# Question 4


x[is.na(x)] = 0 codes for any value being listed /associated with NA to be 0. IN other words, when NA is written, 0 is the output. The nrom = 3 gives the output containing the number of rows that are present in the data frame. since NA=x, and the number of NA is 3, we should get an output of NA, Na, NA being 0, 0, 0. So this code would generate 3 rows for NA , NA, NA, and have them all equal to 0. 



# Question 5 

```{r}
mpg_2 <- 
    ifelse(mtcars$mpg  < 16, "Low",
           ifelse(mtcars$mpg < 21, "Low_Intermediate",
                  ifelse(mtcars$mpg < 26, "High_Intermediate", "High" )))
  mpg_2 
  
  mtcars$mpg_2 = mpg_2
  
```


